%______________________________________________________________________________________________________________________
% @brief   industry resume for summer 2012
\documentclass[line]{resume}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Jackie Kay}
\begin{resume}  %_________________________________________________________________________________________________________
    \rightline{email: jacquelinekay1@gmail.com}
%______________________________________________________________________________________________________________________
% Education
\section{\mysidestyle Education} 
\textbf{Swarthmore College} \hfill \textbf{GPA: 3.54 (Computer Science: 3.67)}\vspace{1 mm}\\
    Expected Graduation: May 2014\\
    Computer Science Major, Double Minor in Engineering and Mathematics
     
\textbf{Relevant Coursework:} Fundamentals of Digital Systems, Data Structures and Algorithms, Mobile Robotics, Computer Vision, Theory of Computation, Natural Language Processing, Computer Architecture, Humanoid Robotics, Computer Networks, Artificial Intelligence\\ \\
\textbf{Languages:} Proficient in Java, C/C++, Python and Matlab; familiar with Javascript, Common Lisp, and Perl.
%______________________________________________________________________________________________________________________
% Projectsg
\section{\mysidestyle Projects}
\textbf{Camtango} \hfill\\
Singlehandedly released Camtango for Android, an event-based photosharing application. Handled asynchronous threading, image processing, user interface, server calls, and SQLite databases.\vspace{0.5mm}

\textbf{OpenSwype} \hfill\\
Utilized computational geometry and natural language processing techniques to implement a continuous stroke input (``Swype") keyboard for Android phones. \vspace{0.5mm}
%\textbf{Eigencats} \hfill\\
%Wrote a data curation routine to transform a data set of cat pictures. Utilized principal component analysis with singular value decomposition on the data set for feline facial recognition.\vspace{0.5mm}

%\textbf{Augmented Reality Dots and Boxes Game} \hfill\\
%Designed an interface for the pencil and paper game which projects an interactive board onto a whiteboard and takes user-drawn input. Implemented image rectification with homographies and filtering and image classification with normalized correlation. \vspace{0.5mm}

%\textbf{Audio Synthesizer} \hfill\\
%Implemented a synthesizer with a variety of waveform and frequency options which takes user key input to produce music by sending calls to the Linux sound card.\vspace{0.5mm}
%______________________________________________________________________________________________________________________
% Work Experience
\section{\mysidestyle Work Experience}
\textbf{Carnegie Mellon Robotics Institute -- Summer Scholar} \hfill \textbf{Summer 2013}\vspace{0.5mm}\\
Led a project on time-dependent, resource-constrained path planning for an autonomous planetary rover. Designed a C++ simulation modeling rover energy expenditure and thermal levels. Project expected to culminate in a research paper.

\textbf{Swarthmore College Engineering Department -- Robotics TA} \hfill \textbf{Fall 2012}\vspace{0.5mm}\\
Instructed students in ROS, basic Linux usage, and robotics theory. Administered Git repositories for homework backup and submission.

\textbf{Lead Android Developer -- AgileZoom, LLC} \hfill \textbf{Summer 2012}\vspace{0.5mm}\\
Responsible for development and publication of all Android products for AgileZoom, Camtango and ici.

%\textbf{Swarthmore College Engineering Department -- Research Intern} \hfill \textbf{Summer 2011}\vspace{0.5mm}\\
%Designed a utility for selecting and storing color profiles from a robot’s field of view to aid computer vision tasks. Coded data structures for occupancy grid mapping. Simulated wireless signal strength localization in MATLAB and C++.
%_______________________________________________________________________________________________________________
% Honors and Awards

\section{\mysidestyle Honors and\\Awards} 
\textbf{RISS REU} \hfill \textbf{2013}\\
Competitive NSF research grant for undergraduates from the Carnegie Mellon Robotics Institute.

\textbf{William Plumer Potter Fiction Award} \hfill \textbf{2013}\\
Swarthmore Department of English Literature's prize for best student short story.

\textbf{Hurd Summer Research Fellowship} \hfill \textbf{2011}\\
Competitive fellowship for undergraduate research in the sciences and engineering.\\

%_____________________________________________________________________________________________________
\end{resume}
\end{document}
